\subsection{Run-time results}
\label{ssec:run-time}

\begin{table}[H]
  \begin{tabular}{| p{2.5cm} | p{2.5cm} | l | l | l | p{2cm} |}
    \hline
    \textbf{Alignment metric} & \textbf{No. of \newline iterations} & \multicolumn{3}{ |l| }{\textbf{Time to run (secs)}} & \textbf{Average time per 1 iteration} \\ \hline
      \multicolumn{2}{ |c| }{} & 5 iterations & 10 iterations & 20 iterations & \\ \hline
      \multirow{3}{*}{Shannon} & BI-RADS I & 6.4 & 11.9 & 23.5 & \textbf{1.22}  \\
                               & BI-RADS II & 8.7 & 16.11 & 30.0 & \textbf{1.62} \\
                               & BI-RADS III & 11.8 & 21.2 & 40.7 & \textbf{2.17} \\
                               & BI-RADS IV & 8.9 & 15.5 & 29.9 & \textbf{1.61} \\
        \hline
        \multirow{3}{2.5cm}{Non - Probabilistic} & BI-RADS I & 135.2 & 277.2 & 573.6 & \textbf{27.81} \\
                                             & BI-RADS II & 214.6 & 425.8 & 893.8 & \textbf{43.40} \\
                                             & BI-RADS III & 275.5 & 595.3 & 1243.0 & \textbf{58.93} \\
                                             & BI-RADS IV & 143.3 & 324.4 & 706.4 & \textbf{32.14} \\
          \hline
          \multirow{3}{*}{Hybrid} & BI-RADS I & 19.3 & 38.3 & 76.1 & \textbf{3.83} \\
                                  & BI-RADS II & 30.2 & 56.9 & 108.7 & \textbf{5.72} \\
                                  & BI-RADS III & 40.6 & 76.5 & 150.6 & \textbf{7.77} \\
                                  & BI-RADS IV & 25.6 & 50.1 & 98.6 & \textbf{5.02} \\
            \hline
  \end{tabular}
  \caption{Run-time statistics for each set over 5, 10 \& 20 iterations.}
  \label{table:run-time}
\end{table}

Table \ref{table:run-time} outlines the run-time statistics for each input set, along with the average time taken to run 1 iteration for each set.

When comparing run-times to the number of images congealed, there is a clear correlation between the number of images being congealed and the length of the run time (e.g. Set 3: BI-RADS III), with some algorithms on average taking twice as long to run 1 iteration. This is to be expected due to the larger amount of information to be processed upon each iteration as each image is aligned with the other.

Shannon entropy has the quickest run-time of the three algorithms. This is likely to be due to the implementation of a lookup table - something which could have been considered for the two fuzzy entropy algorithms.

Non-Probabilistic can be seen to be much slower than its counterparts. This could be due to implementation, however when analysed alongside the entropy result, it could be perceived that the increased accuracy the algorithm provides comes with a compromise on the run-time. This is a trade-off that the user would have to consider when aligning images.

Hybrid entropy has admirable run-time statistics given the complexity of the mathematics needed to compute the entropy value. However the execution times can be seen to rise when the count of input image is increased (e.g. Set 3: BI-RADS III), with a runtime of 3.6 times that of Shannon entropy per iteration.
