%TC:ignore
\chapter{Function Outlines}
\label{appendix:code}

\section{New Functions}

\noindent \textbf{membership.m}
Function to handle the creation and calculation of 3 trapezia fuzzy sets as utilised by Non-Probabilistic entropy.

\noindent \textbf{hybridMembership.m}
Function to handle the creation and calculation of 2 trapezia fuzzy sets as utilised by Hybrid entropy.

\noindent \textbf{TESTmembership.m}
Test function to hold and run unit tests associated to both \texttt{membership.m} and \texttt{hybridMembership.m}.

\noindent \textbf{hybrid.m}
Function which calculates the Hybrid entropy for the input images.

\noindent \textbf{TESThybrid.m}
Test function to hold and run unit tests associated to \texttt{hybrid.m}.

\noindent \textbf{nonProbabilistic.m}
Function which calculates the Non-Probabilistic entropy for the input images.

\noindent \textbf{TESTnonProbabilistic.m}
Test function to hold and run unit tests associated to \\ \texttt{nonProbabilistic.m}.

\noindent \textbf{pgm2bigPgm.m}
Script which takes a directory of images, and saves 1 image containing them all.

\noindent \textbf{TESTpgmCreation.m}
Test function to hold and run unit tests associated to \texttt{pgm2bigPgm.m}.

\noindent \textbf{removeMarker.m}
Function which handles the removing medical markers \acrshort{GUI}`s functionality.

\noindent \textbf{Enantiomorph.m}
Function which handles the main \acrshort{GUI}`s functionality.

\section{Modified Functions}

\noindent \textbf{incrTrans.m}
This function finds an incremental change in the transformation. It also helps the \Gls{Congealing} algorithm in running the correct alignment metric selected by the user.

\noindent \textbf{binaryCongeal.m}
This function takes in the series of images wanting to be congealed and returns the adjusted input images, the mean images, the matrix of transformations, and the array of entropy values after congealing.

\noindent \textbf{testCongeal.m}
This function runs the main congealing algorithm. It also loads in the series of images, resizes them appropriately and runs the \texttt{binaryCongeal.m} function, passing in the correct parameters.

\section{Existing Functions}

\noindent \textbf{fastEntLookup.m}
Function which creates the Shannon entropy lookup table and returns the entropy after comparing it against the input images.

\noindent \textbf{saveSeries.m}
Function which saves the pgm files out in the correct order and with the header needed for \texttt{loadSeries.m}.

\noindent \textbf{loadSeries.m}
Function which loads in the large concatenated pgm file needed for Congealing.

\noindent \textbf{showSer.m}
Function which transforms the 3D array of image values into a figure with each iteration`s mean images / the adjusted input images.

\noindent \textbf{getXfrm.m}

\noindent \textbf{getXfrms.m}

\noindent \textbf{computeXfrmImg.m}

\noindent \textbf{computeXfrmImgs.m}

%TC:endignore
